\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{float}
\setlength\parindent{0pt}

\title{
\vspace{-20.mm}
My Journal on My Research Work}
\author{Hasini Gunasinghe (huralali@purdue.edu)}
\date{}

\begin{document}
\maketitle

\section*{RahasNym}
Until 12th Feb, I mostly worked on improving the paper to be submitted to SACMAT.

\pagebreak

\section*{Biometrics Research Work}
\subsection*{Android Development:}

\subsubsection*{Some useful links for study android dev:}
\begin{enumerate}
 \item Starting another activity: http://developer.android.com/training/basics/firstapp/starting-activity.html
 \item Intents and intent filters: http://developer.android.com/guide/components/intents-filters.html
 \item Interactions between apps: http://developer.android.com/training/basics/intents/index.html
 \item Layouts: http://developer.android.com/guide/topics/ui/declaring-layout.html
 \item Build System: http://developer.android.com/sdk/installing/studio-build.html, 
http://developer.android.com/tools/building/configuring-gradle.html
 \item Intent Class spec: http://developer.android.com/reference/android/content/Intent.html
 \item Android Security Tips: http://developer.android.com/training/articles/security-tips.html
\end{enumerate}

\subsubsection*{RoadMap:}
\begin{enumerate}
 \item Get two activities in an app communicate. DONE. 1st March.
 \item Get two apps communicate and return result. DONE. 14th March.
 \item Get an app to communicate with a remote REST service. DONE. 17th March.
 \item Integrate ZKP.
 \item Run perf test for ZKP with a remote party with static identity.\\
 Perf test config: Connect laptop to network through wired connection. Run tomcat+services in Windows (so there wont be port forwarding overhead.)
 \item Look at the new trend in replacing passwords with FRT and re-write the introduction of the journal.
 \item Send the update to Prof: Perf results + introduction re-written.
 \item How to access TrustZone.
 \item Look at secure coding of android applications (downloaded).
 \item Biometrics work follow.
\end{enumerate}

\subsubsection*{Wed Jan 20}
I installed Android studio. I referenced this good tutorial: http://www.androidauthority.com/first-android-app-what-you-need-to-know-619260/\\
However, in my Ubuntu, I got an error from android studio saying that SDK or libraries could not be installed. \\
Then this was the solution: http://stackoverflow.com/questions/28804863/android-studio-how-to-install-android-platform-tools-on-ubuntu-14-04-64-bit
It was because Android needs 32 bit libs and I have a 64 bit Ubuntu.\\
Here are some tips I found to make the emulator fast:
http://developer.android.com/tools/devices/emulator.html\#vm-linux

\subsubsection*{Feb 19}
Emulator runs Android in a kind of virtual machine, as an Android phone with an Intel processor. This is faster than emulating an ARM processor on 
your PC.

\subsubsection*{Feb 22}
After lunch, I worked on the mobile app dev. I am still at the very very beginning. Followed first app tutorial till end, and got a problem when 
running in the emulator. Emulator needs KVM \textit{emulator: ERROR: x86 emulation currently requires hardware acceleration!
Please ensure KVM is properly installed and usable.
CPU acceleration status: KVM is not installed on this machine (/dev/kvm is missing).} \\

Then I tried to install KVM based on this tutorial:\\
https://software.intel.com/blogs/2012/03/12/how-to-start-intel-hardware-assisted-virtualization-hypervisor-on-linux-to-speed-up-intel-android-x86-emul
ator

However, there seems to be problems. \\
1. When I ran the command at the beginning of that tutorial to check if the CPU supports KVM extensions, I get 
the output as NO. However, since the error from Android studio shows some hope, I tried to install it.

2. Then the install command given in the tutorial doesn't work. Then I tried this: whose command works. 
https://www.howtoforge.com/tutorial/kvm-on-ubuntu-14.04/

It seems that now I need to relogin to enable KVM for my user accounts. 

\subsubsection*{Feb 24:}
Since I had issues in running the hello world app in the emulator due to KVM enabling issue, I thought f checking my bios to see if KVM is enabled.\\
Before accessing the bios, I needed to backup my important files in bitbucket. Therefore, I spent sometime backing up my files.\\
Then I spent some fair amount time accessing the bios. First I tried F2 key as mentioned in many online articles which didn't work. Then F12 worked. 
Intel VT is enabled in the bios.\\
Then I checked the VMWare settings. So the problem was VT was not enabled in VMWare. When I enabled it, the emulator ran. But it was damn slow.\\

I searched about how to make the android studio fast. I got some answers:\\
1. http://www.viralandroid.com/2015/08/how-to-make-android-studio-fast.html\\
This suggested either to test in real device or in genymotion emulator: https://www.genymotion.com/download/\\

\textbf{Option 1: } I tried to install genymotion emulator, but it requires VirtualBox to run. Hmmmm. VirtualBox on VMWare!. So I thought of 
first running in the real device and see because I anyway have to install it in a real device.

\textbf{Option 2: } Option 2 is to install genymotion+virtual box on windows, compile the project in Linux and run it in the genymotion 
running in Windows. https://dzone.com/articles/genymotion-simply-best-android \\

I tried to install it in my phone (I upgraded my phone too for this reason. My phone is running Android 4.4.2). But somehow it didn't get installed.
I was so tired by then and went to sleep.\\

\textbf{TODO:}
Read how to make android studio faster:\\
1. https://dzone.com/articles/how-speed-android-studio\\
2. http://www.codeproject.com/Articles/803935/How-To-Make-Android-Studio-Really-Fast-On-A-Window\\


\subsubsection*{Feb 25:}
I continued my attempt in installing in the real device. But I still couldn't.
I found that there is no apk built when I run the project. So the studio complains that no local path exists. So I need to understand what the heck 
is going through the Android build process. See how slow my progress is! :(\\

Oh... Android studio integrated gradle build is a crap!. It didn't even complain that the build was not successful. That is why there was no apk 
local path existed.\\

I ran gradle build from command line according to this tutorial: http://developer.android.com/training/basics/firstapp/running-app.html\\
Steps: \\
1. invoke the assembleDebug build task using the Gradle wrapper script (gradlew assembleRelease).\\
chmod +x gradlew\\
./gradlew assembleDebug\\

I got an error when running ./gradlew: ``libz.so.1: cannot open shared object file'', followed by: ``Exception in thread "png-cruncher\_4" 
java.lang.RuntimeException: Timed out while waiting for slave aapt process, try setting environment variable SLAVE\_AAPT\_TIMEOUT to a value bigger 
than 5 seconds''.\\
It seemed that both errors are due to not installing the library: zlib1g as mentioned in: 
http://stackoverflow.com/questions/21256866/libz-so-1-cannot-open-shared-object-file\\
After doing: sudo apt-get install zlib1g:i386, the gradle gave me: BUILD SUCCESSFUL Total time: 1 mins 16.537 secs. :)\\

2. Then I wanted to deploy the app in my phone also from the command line (mentioned in the same above tutorial).\\
Added android-sdk/platform-tools to PATH and ran: adb install app/build/outputs/apk/app-debug.apk\\
Yeyyy... I got my first android app installed on my phone! :) Now the floor is mine to do cool stuff.\\

Command line worked so smooth compared to crappy android studio. \\
\textbf{Commands to build and run in the phone:}\\
./gradlew assembleDebug\\
adb install -r app/build/outputs/apk/app-debug.apk\\

I went step further, I editted my app and tried to run again in my app. First I failed because it was already installed. Solution was to install it 
with the -r option. :)

\subsubsection*{29th Feb:}
I didn't do much. I re-organized my research journal and went to apt with the hope of working more. But I was so tired and went to sleep.

\subsubsection*{1st March:}
Learned many new things. At the end of the day, I have an app running in my phone with two activities linked 
(http://developer.android.com/training/basics/firstapp/starting-activity.html).
\begin{enumerate}
 \item How to add a new activity and what are the other parts of an android project related with an activity: AndroidManifest.xml, the activity.xml 
under the res/layout folder, strings.xml file.
 \item How to change the layout of an activity and use layout weight. 
 \item How layouts are related with parent-layout (as indicated in the activity\_layout.xml and AndroidManifest.xml).
 \item View and ViewGroups.
 \item How to add a method for a view to be responsive. Method should satisfy following:\\
 Be public. Have a void return value. Have a View as the only parameter.
 \item Intent: \\
 create Intent : newIntent(), \\
 add name-value pairs to it: intent.putExtra(name, value),\\
 start activity passing the intent: 
 startActivity(intent), \\
 receive data sent thru an intent: getIntent(), getStringExtra(name). 
 \item Accessing View elements of an activity through:\\
 findViewById(R.id.<id\_name>)  method.
\end{enumerate}

\textbf{Next step:} getting two apps to communicate. I might want to understand intents and intent filters properly before that.

\subsubsection*{3rd March:}
I learnt how to invoke an app from one app that accepts an intent and return a result.\\
However, I could not implement. I am writing down notes while I am reading a tutorial which slows me down. IDK\\
Anyway, below is something I can modify to abstract the high level idea and metion in the implementation details of the journal.\\

\textbf{Intents:}\\
- Following is from: http://developer.android.com/guide/topics/manifest/manifest-intro.html\#ifs\\
The core components of an application (its activities, services, and broadcast receivers) are activated by intents. An intent is a bundle of 
information (an Intent object) describing a desired action — including the data to be acted upon, the category of component that should perform the 
action, and other pertinent instructions. \\

- Android locates an appropriate component to respond to the intent, launches a new instance of the 
component if one is needed, and passes it the Intent object.\\

- Components advertise their capabilities — the kinds of intents they can respond to — through intent filters. Since the Android system must learn 
which intents a component can handle before it launches the component, intent filters are specified in the manifest as <intent-filter> elements. A 
component may have any number of filters, each one describing a different capability.\\

- An intent that explicitly names a target component will activate that component; the filter doesn't play a role. But an intent that doesn't specify 
a target by name (implicit intents) can activate a component only if it can pass through one of the component's filters. 

\subsubsection*{14thMarch:}
- I created a new project with two app-modules : authapp and clientapp and started adding the basic logic to it.\\
Actually, even this simple thing took me several hours to get right. Thing is, when I create a new android  project, the app in that project is named 
just 'app', and doesn't hold the name that I give at the creation time. Although I tried renaming etc, didn't work. So, what I did was: create the 
android project, leave the default app that gets created, and create two new modules for my use with the names that I want.\\

- I made the client app to invoke the auth app, passing the SP URL to it.\\
Auth app printed the passed infor and returned the session id to the client app which the client app printed in a toast.\\
 \textbf{Troubles:}\\
 First the app crashed because the name of the method written for the button didn't match.\\
 Then I learned to debug the app while it is running in the phone.\\
 Then I couldn't invoke the second app because the way I have declared the data field in the intent filter didn't match.\\
 Everything worked after I removed the data field from the intent filter.
 
\subsubsection*{15thMarch:}
I couldn't do much. But I searched for some good tutorial to learn how to invoke a REST service from mobile app.\\

\textbf{Then I found this good and complete tutorial 
(http://programmerguru.com/android-tutorial/android-restful-webservice-tutorial-how-to-call-restful-webservice-in-android-part-3) which uses 
async Http client (http://loopj.com/android-async-http/) which is based on the apache Http client.}

I also drew the sequence diagrams for enrollment and authentication using ZKP, before starting implementing. Then I realized that we need an 
additional step to allow users to obtain:\\
\begin{itemize}
 \item different IDTs with different To fields, with same commitment. For this, user just have to send the IDT issued by the IDP at the enrollment 
time with To field having IDP name and carry out ZKP to prove that the token belongs to him/her.
 \item different IDTs with different To fields and different commitments to achieve unlinkability. For this, user needs to send a biometrics capture, 
IDP runs it trough BID generator and create a new commitment. \textbf{We follow this approach because we do not store BID anywhere.}.
\end{itemize}

\subsubsection*{16thMarch:}
I started writing a REST service to be invoked by the android app. \\

I thought of going for Jersey rather than CXF because, jersey is said to be more light weight and meant for REST, compared with CXF which is more 
focused on SOAP.\\

I followed these tutorials to learn. It was very easy. You only need web.xml.\\
\begin{itemize}
 \item (2015) http://tutorial-academy.com/restful-webservice-jersey-maven/
 \item (2011) http://www.mkyong.com/webservices/jax-rs/jersey-hello-world-example/
 \item (Not so good, but it has client code.) http://www.vogella.com/tutorials/REST/article.html\#installation\_jersey
 \item (Jersey modules and dependencies:) https://jersey.java.net/documentation/latest/modules-and-dependencies.html
\end{itemize}

\textbf{Troubles:}\\
I got an issue of not being able to access the REST service. It was due to the fact that in servlet filter pattern, we need to specify the path 
ignoring the path until the webapp's name.\\

Oh god, now I have basic REST service written in jersey to play around with.\\

I read a bit about android http clients before start writing the client side for the REST service.\\
This article gives a very good history: https://packetzoom.com/blog/which-android-http-library-to-use.html\\
But it doesn't mention about async http client. Also, the quora thread doesn't mention about it: 
https://www.quora.com/What-is-the-best-library-to-make-HTTP-calls-from-Java-Android

From the first article above, it seems that OkHttp is promising, but it seems that it requires some additional things to get REST, json, images etc 
working such as Retrofit..\\

The reason I didn't go with Volley: https://developer.android.com/training/volley/index.html (although it is from google) is that it has very few 
number of threads as per the first article above. But the plus point is that it is said to work with all types of devices including low power 
devices.\\

I thought of going with async http client as it is based on Apache HTTP client, but the only problem is that it says it is compatible with Android 
API 23 and higher. Let's see. If problematic, I will switch to OkHttp or Volley.\\

\textbf{HTTPS clients with Async Client:}\\
http://stackoverflow.com/questions/21833804/how-to-make-https-calls-using-asynchttpclient\\

\textbf{Troubles and Solutions:}
\begin{enumerate}
 \item The first problem I got was: the dependency for the async http client was not resolved by Android studio, although I could build the project 
using command line gradle. I tried several things: File->Invalidate Cache and Restart etc. Only thing which worked was: moving the entry for async 
http client one entry up in the gradle script. It was this stackoverflow thread which helped me: 
http://stackoverflow.com/questions/19508649/android-studio-says-cannot-resolve-symbol-but-project-compiles\\

 \item There was another wired issue: I couldn't assign response's values to local variable defined in onAuthButtonClicked method of AuthActivity of 
AuthApp, because the response received in the onSuccess method of an inner class of async http client. I had to declare the variable as final and had 
to make it an array too. Related stackoverflow thread: 
http://stackoverflow.com/questions/27558425/local-variable-access-to-inner-class-needs-to-be-declared-final

 \item So, finally, I was able to build the mobile app with async http client. But I wanted to return the response as JSON. Actually, Jersy has very 
good support for object to json conversion. This tutorial is a good starter: 
http://www.mkyong.com/webservices/jax-rs/json-example-with-jersey-jackson/.

\item Troubles continues: I couldn't invoke the rest service from the mobile app. I left Hicks undergrad, after my first try. \\
Came home, did exercise, cooked, ate, talked with amma, thaththa and Thil and tried again.\\

I could access the service through host (windows) browser, but not from android. I debuged, and got the exception as: connection time out. Actually, 
in order to debug, I had to avoid the normal route of client app invoking the auth app, and implement AuthActivity invocation from the mainactivity 
of the Auth app itself,
Silly me 
didn't realize that the IP of VM is not visible to outside. I went to sleep thinking it might be the reason that async HTTP client is said to be 
compatible only higher than API 23 or something\\

\textbf{Opportunity:} Prof. asked me to write a proposal for PRF. I would like to write it. I need to steal some good time from my busy schedule to 
write down one of my ideas for the proposal. I am thinking of writing the GC idea for biometrics authentication which could avoid some of the 
drawbacks in our current method. I need to read the previous (NDSS paper) and get an idea where things stand today. May be I should spend the 
research three days of next week for writing the proposal (Sunday, Tuesday and Thursday).

\subsubsection*{17th March}
Today morning I got up at 7.15 and thought that I will do only PL, cause I spent whole day yesterday on research proj. But I missed the bus at 8am so 
I thought I will try to connect mobile app to phone till next bus. \\

The journey:\\
\begin{enumerate}
 \item First I tried to access the tomcat home page from phone and ipad browsers, which failed.
 \item From this thread (http://stackoverflow.com/questions/9887621/accessing-localhost-of-pc-from-usb-connected-android-mobile-device), I tried to 
make a hotspot in phone and tried to connect to it from laptop. But, as soon as the hotspot is made, the normal internet connection in phone goes 
off. Seems like it should be made using the data connection in the phone. So that option is out.
\item From some other reading, I realized that firewall may be blocking. Then I tried to disable the firewall and tried to access the tomcat home of 
server in VM Ubuntu, from phone-no hope. Silly me didn't try to first access a server in host OS and see at least if it works.
\item Then I added an inbound rule in firewall to allow connections on port 8080, since I am scared of disabling firewall. It didn't work either.
\item I installed tomcat on windows and tried to access its home page from phone browser. It worked only after disabling the firewall. But still no 
luck accessing the tomcata in Ubuntu VM.
\item Then my understanding improved and I checked VM settings. The networking is enabled through NAT, which doesn't make VM visible to outside, that 
is why the phone couldn't access the tomcat running in VM. Hmmmmmmmmmmmmmmmmmmmmmmmmm.
\item The solution was to make VM settings such that network mode is: bridge. But so so badly, for some mysterious reason, all the real network 
adaptors are not made available to VM Ware settings. I do not know if it is done by Windows 8 or if it is due to some other reason.\\

I should check : just like enabling virtualization for CPU, whether I need to enable something from bios. But bridging for VMs seems to be something 
that trivially work for others, but not for me.\\

Following are some links that I found useful when searching to get over this issue:\\
- Good article: https://pibytes.wordpress.com/2012/11/16/vmware-workstation-networking-basics/\\
- Threads: http://askubuntu.com/questions/629457/i-cant-connect-to-virtual-ubuntu-server-from-smartphone, 
http://askubuntu.com/questions/237461/how-do-i-access-ubuntu-server-running-in-virtualbox-from-outside\\

As this thread (http://superuser.com/questions/810097/vmware-player-bridged-networking-no-longer-works-host-win8-1-guest-mint-17-l) says: lot of 
Virtual Box related adaptors are made available, which I unchecked in Bride settings, but still no luck.\\

As this thread (http://stackoverflow.com/questions/4601762/how-to-connect-wireless-network-adapter-to-vmware-workstation) suggests, I also tried 
making a loop back, as described here: (https://4sysops.com/archives/how-to-install-loopback-adapter-in-windows-8/). Still no luck.

\item My final fall back was to use same old NAT for VM and use port forwarding, as suggested in this thread: 
http://stackoverflow.com/questions/10355702/connecting-to-apache-web-server-that-is-running-on-a-vmware-from-any-device-in-t\\
The tool made available in this site (http://www.quantumg.net/portforward.php): saved me finally. I hope I can trust that is not a malware. Even if it 
is, I have no other option. \\

Well, I have one, which is: run tomcat on Windows->copy .wars to it and access from phone. But I feel it will be very time consuming during the dev 
process. It will be good for perf testing.

\end{enumerate}



\end{enumerate}

 


\pagebreak
\subsection*{To Dos:}
\begin{enumerate}
 \item Study the mobile phone's security architecture and find about the latest work in the secure architecture/trust zone.
 \item Discuss the attack surface/vulnerability window and argue that it is very small.
 \item Look at Daniel's journal paper to see how to prepare a journal paper.
\end{enumerate}

\subsection*{Literature Survey:}
\subsubsection*{Feb 19}
Today, I was just searching zero knowledge biometrics authentication for remote services. I got a bunch of results - papers and a commercial
product.\\
\textbf{Sedicii}\\
This commercial product : sedicii (https://www.sedicii.com), seem to be doing exactly what I have done: ZKP based identity verification/authorization.
They say that they do credit card authorization as well as biometrics authorization in ZKP - exactly my two works.
They have not described how they do biometrics authentication in ZKP, however, it should be similar to their website loging scenario:
I have written how their credit card authorization is comparable to ours in my RahasNym journal.

\subsection*{Brain Storming:}
\subsubsection*{Feb 19}
Lot of biometrics based authentication mechanisms are defined for authenticating to devices. Once authenticated into the device, different services 
that the user accesses are already logged in with username/password security. In such cases, critical remote services are relying on the device 
biometric authentication, which is not usually strong.\\
\textbf{TODO:} \\ See how device biometrics authentication works in Android and Apple.\\
Also, if a malware is installed by some mistake by the user, client of the remore service is at risk (password can be stolen, session stolen etv.).\\ 
\textbf{TODO:}\\
See how bank apps work in mobile devices.\\

This shows the requirement for remote services to have their own authentication of user to make sure that the genuine user invokes some request, with 
strong verification, beyond usernam/password, and without relying on device autentication.\\
ZKP is a good candidate. There are some previous works, suffers from some drawbacks.\\ Main issue is identity is not static.\\
The works differ by the approach they address this non-static nature of the biometrics.\\

This should be a standard mechanism, that any app resides in user's device-communicating with the remote service can integrate easiliy.\\
\textbf{TODO:}\\
See this could be developed as a service in Android which could be invoked by other apps.\\

\textbf{Contributions of our work:}
\begin{itemize}
 \item Secure protocol for remote authentication using biometrics. Preserves good properties of biometrics (i.e: uniqueness). Avoids non-desirable 
properties of biomertics (i.e: non-repeatability, non-revocability).
 \item Prototype implementation that is a proof of concept. That can be integrated to any app.
 \item Security Analysis and Performance Analysis.
\end{itemize}

\subsubsection*{Feb 20}
I started documenting what I wrote down on paper during the weekend. I felt I need a brainstorming/mind mapping tool. And I got FreeMind and noted 
down different aspects.\\

\subsubsection*{16th March}
I found these articles which talks about Amazon, Alibaba and Google adopting selfies or FRT to make payments instead of password. But I think it is 
bad. Coz now, instead of passwords, you store templates to pattern match, which has higher risk than passwords, coz passwords can change and you can 
use different passwords at different SPs unlike your frt template.\\

\begin{enumerate}
 \item https://thestack.com/security/2016/03/15/amazon-wants-to-replace-passwords-with-selfies-and-videos/
 \item https://thestack.com/cloud/2016/03/03/google-hands-free-facial-recognition-trial-san-francisco/
 \item https://thestack.com/security/2015/03/16/alibaba-demonstrates-facial-recognition-payment-system-at-cebit/

\end{enumerate}


\pagebreak
\section*{New Ideas:}

I attended Prof. Dongyan Xu's research award talk. I liked how he presented his research work as branches of a tree.

\subsection*{PrivBioAuh and PrivBioGeneAuth}
I can have two projects under the umbrella: PrivBioAuth. Two will be: PrivBioMTAuth and PrivBioGeneAuth.\\

\subsection*{How to address the security issues in health care data collected from IoT devices using biometrics.}
Professor suggests to see how to generate keys from biometrics to protect the medical data.

\subsection*{Fuzzy Zero Knowledge Scheme:}
\subsubsection*{Feb 23:}
I worked on the research the whole afternoon after lunch - but on an apparently useless one. I tried to comeup with a fuzzy zero-knowledge protocol 
based on the ideas from fuzzy identity based encryption. But I had no luck.

I need to look at fuzzy commitment and fuzzy vault before talking about this with anyone else.\\
Professor mentioned we can talk with Professor Atallah or Italian professors.\\

\subsection*{Storing the machine learning model by encoding it in a garbled circuit}
\subsubsection*{Feb 19}
- I got an idea yesterday that I could use the same method of obtaining a circuit from IDP for authentication verification later.\\ 
But the circuits can be used only once, which is a problem.\\
\textbf{QUESTION:}\\
- Good question I can ask in the summer school: are garbled circuits re-usable?\\

\textbf{REFERENCES:}\\
This is a very nice project website - a resovair of resources. http://www.mightbeevil.org/ and http://www.mightbeevil.org/mobile/


\pagebreak
\section*{Meetings with the advisor:}
\subsection*{Feb 25:}
\begin{itemize}
 \item I spent lot of time getting ready for the meeting - how I explain what I did, and my ideas to the Professor. At the beginning, she was not in 
a very good mood. But the end was very good.
\item It is ok to have 35\% overlap with the conference paper. If I could get the implementation on the mobile phone and do the Performance 
evaluation, that would be an excellent extension for the journal paper. Need to get it by the end of this semester. Usually we do not submit new work 
for journals. Only extensions.
\item I need to look at Daniel's journal to see how I can prepare my journal paper.
\item I need to study the mobile phone android security architecture and write about it.
\item Professor mentioned about the new idea of protecting the medical data.
\item Professor was interested in two of my new ideas. Professor mentioned we can ask Prof. Atallah or her Italian collaborators. She said it is a 
very specialized area.
\item Professor gave me the two recommendations for the communication requirement and the travel grant application.
\end{itemize}

\subsection*{Next Meeting:}
I should mention about the issue of recovering from memory images. May be we can ignore it for the moment.\\
Can we mention about the counter measures that we took in order to avoid the threats arise due to specifics of our architectural decisions and the 
specifics of the framework?\\
May be we can mention them as the security best practices for client implementations.



\end{document}