\documentclass[10pt]{article}
\usepackage[letterpaper,top=1in,bottom=1in,left=1in,right=1in]{geometry}
%\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{float}
\setlength\parindent{0pt}

\title{
\vspace{-20.mm}
Privacy Preserving Biometrics based Remote Authentication Protocol for Mobile Devices}

\begin{document}
\maketitle
\section{Motivation:}
There has been a major shift from traditional passwords based authentication to biometrics based authentication in consumer applications in the 
recent past as major service providers such as the leaders in banking~\cite{citi, hsbc, usaa}, credit cards~\cite{mastercard} and 
e-commerce~\cite{amazon, alibaba} are adopting biometrics to authenticate users.
Biometrics is a strong factor of authentication due to its ability to uniquely identify an individual. Different 
vendors have adopted it for different motivations, for examples, Amazon uses selfies based on facial recognition techniques to avoid the difficulty 
in typing passwords to authenticate transactions in mobile devices with small screens~\cite{amazon} and  Master cards has adopted it in order to 
drastically cut-down the cost of false decilned transactions~\cite{mastercard}.

Two main contexts in which biometrics is being used for authentication are: in-person authentication~\cite{google} and remote 
authentication~\cite{hsbc}. In the first case, user is present at the authenticator's premise when authentication is performed and a device of the 
autheticator captures the 
biometrics. In the second case, authentication is performed over the network and the biometrics is captured by the user's device. 
While there are common challenges w.r.t both cases due to the sensitivity (being tightly coupled with one's identity) non-repeatability (no 
two biometrics samples of the same individual match exactly) and non-revocable (inability to cancel/renew) nature of biometrics, the second case 
involves more challenges than the first one in terms of liveliness verification of the biometrics to avoid spoofing attacks, secure 
transmission of the authentication information and security of the user's device. Furthermore, remote biometrics based authentication is being widely 
used since online-banking and e-commerce applications are increasingly adopting it.

Aforementioned commercial authentication systems that are being deplyoed today, inherit key security 
concerns irrespective of the fact that they incorporate state-of-the-art facial/voice recognition algorithms and liveliness verification techniques. 
First, since users' biometrics templates are stored in the server databases for matching during the authentication, they become major targets 
of attackers.
For examples, in Google Hands Free system~\cite{google}, user's picture taken at the authentication time is matched with the user's Hands Free 
profile picture and in Citi bank system, user's pre-recorded voice samples are matched with the voice captured when the user call in. Second, 
multiple third party service providers are storing different biometrics traits of the same user (such as face, voice and fingerprint) for their 
proprietaty authentication protocols. This creates multiple points of vulnerability on one's biometrics identity, due to 
linkability~\cite{linkability}. Third, the current protocols require the users to send a raw biometrics sample over the network each time the user 
remotely authenticates using biometrics, which is not desirable.
%as such biometrics samples reveal sensitive features of the user's biometrics which are used to uniquely identify an individual. 
Stolen biometrics templates from the server databases or from the authentication channels lead to identity theft which poses severe threat to user's 
digital identity, compared to the case in which a password is stolen, because biometrics samples reveal sensitive features of the user's 
biometrics identity which can not be revoked.
%non-revocable nature of the biometrics.

Therefore, it is best to avoid storing and transmitting sensitive biometrics information during authentication, when developing a secure biometrics 
based remote authentication protocol.
%because we can not solely rely on 
%encryption to protect biometrics databases and authentication channels as there have been many instances of 
%password breaches in the past, although such techniques were used to secure passwords during storage and transmission.
The second issue mentioned above can be avoided by getting a trusted identity provider (IDP) to enroll user's biometrics identity~\cite{google, 
identityX}. However, if the IDP is involved in each transaction that the user authenticates, it undermines the user's privacy since the IDP gets to 
know about different transactions that the user performs with different service providers.
  
To address aforementioned security and privacy concerns, we aim to develop a biometrics based remote authentication protocol with following 
characteristics:
\begin{enumerate}
 \item User's biometrics identity is enrolled with only a trusted IDP (i.e: biometrics is not stored with multiple service providers).
 \item Sensitive features of user's biometrics is not stored anywhere.
 \item Sensitive features of user's biometrics is not revealed during authentication.
 \item After the initial enrollment with the IDP, users can carry out biometrics based authentication with multiple service providers without 
involving the IDP. (i.e: user-centric authentication protocol as opposed to traditional IDP-centric authentication protocol).
 \item Efficient in terms of computation and communication in order for it to be carried out from user's mobile devices.
\end{enumerate}

In what follows we describe our roadmap of realizing the goal of developing a privacy preserving biometrics based remote authentication protocol with 
the aforementioned characteristics.

\section{Past and on-going research work:}
We found Zero Knowlede Proof (ZKP) of identity to be a suitable cryptographic primitive to be used along with a secure commitment 
scheme~\cite{pedersenCommitment}, in order to authenticate without revealing any biometrics information to the SP. The concept of ZKP of identity, 
first proposed by Feige, Fiat and Shamir~\cite{fiat-shamir} in 1988, has been used to develop numerous identity based authentication 
schemes~\cite{idemixConcepts}.

(Write about the ZKPK based solution that we have proposed and currently working on in implementing in the mobile device, to achieve the above 
goal.)
\subsubsection*{2.1 Overview of the solution:}
TODO:

\section{Next research goal:}
In the aforementioned solution that we develop to achive our goal mentioned in Section 1, we assume the support of Trusted Execution Environment 
(TEE) in the user's mobile device to securely store the artifacts obtained from the IDP during the enrollment phase and to execute BID generation 
using the classifier during the authentication phase. TEE isolates the storage and execution from other applications which provides further 
protection in addition to encrypting the artifacts during storage and which is being used by Apple touch ID and android fingerprint authentication 
framework as well.
While there are extensive research on the develpment of TEE technology~\cite{tee}, there are attacks being discovered~\cite{blackhat} on them too. 
Since widely used implementations of TEE technology such as ARM's TrustZone are proprietary and not disclosed for public review, the level of 
assurance provided against a given threat model is unclear~\cite{armtrustzone}. 

Furthermore, recent advancement in memory forensics techniques~\cite{dimsum}, pose threats on processing sensitive data in the memory of user's 
device in clear text, as it is proved that such data could be recovered from memory images even long after the processing of such data is finished. 
Although it is theoretically possible to clear the memory soon after the processing of sensitive data, it is not practical because it requires 
accurate tracking of each data object in order to clear them upon destruction of the process, which is a very heavy-weight operation 
that no commodity operating system performs.

Therefore, it is at our best interest to develop a privacy preserving biometrics based authentication protocol which achieves all the security and 
privacy goals mentioned in Section 1, based on theoretical foundations and without assuming any hardware security support. Fully homomorphic 
encryption (FHE)~\cite{fhe} is one solution to avoid decryption of sensitive biometrics information during authentication, however, it has certain 
drawbacks to be used in building an authentication protocol with the aforementioned characteristics, as the service provider learns the 
authentication function, which is the classification model in our case, and it needs to obtain the secret key to decrypt the authentication result, 
which in turn allows it to decrypt the biometrics data as well. Yao's garbled circuit~\cite{yaogc}, on the other hand, is a better cryptographic 
building block as it allows secure computation of a function $f$ on input data $x$ to obtain the result $f(x)$ while hiding both the function and the 
input data from the function evaluator.

\subsubsection*{3.1 Related work:}
%\subsubsection*{Related work:}
%What people have already done in this direction:
%- GC for biometrics authentication
%- GC on mobile devices
%- GC for classification
%- Reusabile GC.

\subsubsection*{3.2 Challenges:}
One basic limitation of the original garbled circuit construction is that it offers only one-time usage. Specifically, evaluating a circuit on any 
new input requires an entirely new garbling of the circuit~\cite{reusablegc}. This causes the user to communicate with the IDP each time the user 
needs to authenticate to a service provider, which we need to avoid as per the 4th requirement mentioned in Section 1. The problem of reusing garbled 
circuits has been open for 30 years until the reusable garbled circuit contstruct was proposed by Shafi et. al in 2013~\cite{reusablegc}. This new 
construct looks promising to develop the biometrics based authentication protocol that we target, as it allows the secure authentication artifacts to 
be used multiple times without exposing any sensitive information during the process.
Utilizing this construct in designing and developing our target biometrics authentication protocol, however, requires addressing several challenges. 
Firstly, the scheme poposed in~\cite{reusablegc} is presented in the context of two party secure computation. Although original garbled circuit 
construct can be used in three-party context, it is currently not straight forward to see how the re-usable garbled circuit contruct could be extended 
to three-party protocol, which we need to investigate further. Secondly, all the current efficient implementations of garbled circuits do not support 
this construct, which is currently a challenge when it comes to implemention of the protocol. Therefore, we believe that designing and developing a 
privacy preserving biometrics authentication protocol using this construct will contribute important results to the research literature.

\subsubsection*{3.3 Contribution of this work:}
We aim to produce the following research output:
\begin{enumerate}
 \item Designing a privacy preserving biometrics based remote authentication protocol with aforementioned characteristics, using re-usable garbled 
circuit construct. 
 \item A prototype implementation of the protocol that is able to run in mobile devices.
 \item Security and performance analysis of the protocol.
\end{enumerate}

\section{Background and potential impact:}
- After the current work is over, at the end of this semester, we will have a working prototype of our past approach in the mobile phone. PhD student 
Hasini will be attending a summer school conducted by leaders of secure mpc and oblivious computation research to learn the current-state-of-the-art 
techniques. She has got a travel grant form NSF to participate in this.
- Google ATAP project has accepted a proposal written by us and has funded Purdue.
- Can help make existing biometrics based remote authentication in day-to-day transactions such as online-banking and e-commerce secure, which 
already has a large user base and increasing.\\
- Generalization of this techniques can have impact on other ML tasks where privacy is a concern.
%\pagebreak

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,IEEEexample}
 
\end{document}
